COG-ED Manuscript

### 2022-01-11 06_Paper/COG-ED/Manuscript.Rmd
adapted table name

  # create interaction plot
  h2b_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                               plot.points = T, point.shape = T,
                               x.label = "n back level", y.label = "subjective value",
                               legend.main = "NFC", interval = T) + theme_apa()    
```

@@

The MLM revealed that n-back level was a reliable predictor of SV (`r apa_print(m1_h2b)$full_result$level_cwc`), even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers. 
The results of the MLM are detailed in Table 1. 
`r table_1`
Differences between subjects could explain `r round((icc_h2b*100), digits = 0)` % of the total variance in SVs ($ICC =$ `r round(icc_h2b, digits = 2)`).
However, NFC had no statistically significant effect on SVs (`r apa_print(m1_h2b)$full_result$nfc_cgm`).
The simple slopes analysis revealed a significant difference in slope of n-back level for three different expressions of NFC (Table 2, Figure 2).
`r h2b_ss.table`
`r h2b_ss.plot`
The Johnson-Neyman plot (Figure 2) visualizes the significance of the slope of n-back level at different values of NFC.
The Johnson-Neyman interval is [`r h2b_jn.int`].
Consequently, the slope of n-back level was not significant for individuals with very low NFC values.    
`r h2b_jn.plot`

>>>>

  # create interaction plot
  h2b_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                               plot.points = T, point.shape = T,
                               x.label = "n-back level", y.label = "subjective value",
                               legend.main = "NFC", interval = T) + theme_apa()

@@

The MLM revealed that n-back level was a reliable predictor of SV (`r apa_print(m1_h2b)$full_result$level_cwc`), even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers. 
The results of the MLM are detailed in Table 1. 
`r table_1`
Differences between subjects could explain `r round((icc_h2b*100), digits = 0)` % of the total variance in SVs ($ICC =$ `r round(icc_h2b, digits = 2)`).
However, NFC had no statistically significant effect on SVs (`r apa_print(m1_h2b)$full_result$nfc_cgm`).
The simple slopes analysis revealed a significant difference in slope of n-back level for three different expressions of NFC (Table 2, Figure 2).
`r table_2`
`r h2b_ss.plot`
The Johnson-Neyman plot (Figure 2) visualizes the significance of the slope of n-back level at different values of NFC.
The Johnson-Neyman interval is [`r h2b_jn.int`].
Consequently, the slope of n-back level was not significant for individuals with very low NFC values.    
`r h2b_jn.plot`
